|

### 2021-12-06 03-Chp-Systematic-Review-Methods.Rmd
Working version
End of day:

This analysis sought to address two specific aims. Firstly, as discussed in the introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist. These include randomised controlled trials, observational studies of different design, and Mendelian randomisation studies. However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types. Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association. As such, the primary aim of this analysis was to systematically review all available literature describing prospective analyses, regardless of study design.

Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but can report relevant unpublished analyses. As a sensitivity analysis to this review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).

@@

Eligible studies screened participants for dementia at baseline and excluded any prevalent cases. Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate. No limits were placed on the sample size of included studies. Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the sole exception to this, as it was assumed that health care professionals employed their own expertise when entering used when entering the outcome into the EHR.

Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain information on the study's status. No limitations were imposed on publication status, date, venue or language.

@@

Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) were excluded. Additionally, studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arm were excluded. For example, a study examining exercise + statins versus statins alone would be excluded, but a study examining exercise + statins vs exercise alone would be eligible as the effect of statins can be estimated. Finally, studies using a dietary intervention, for example an omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet. Note that this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.

@@

When searching the bibliographic databases, study design filters (Lines 9-11 in Table \@ref(tab:searchOverview-table)) were employed to try and reduce the screening load. To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.

@@

Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. In addition, the abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing").[@greenhalgh2005; @wohlin2014]

@@

Records were imported into Endnote and de-duplicated using the method outlined in Bramer et al. (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g. those identified as duplicates based on the "Title" field alone).

Following de-duplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. Additionally, I re-screened the same ~10% sample with 3 month lag to assess intra-rater consistency.

Similarly, I completed all full-text screening, with a random ~20% being screened in duplicate by a second reviewer, in addition to any records I identified as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage were recorded. Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague. A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]

@@

How to interpret agreement coefficients is widely debated, and while arbitrary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement. Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrated issues with the screening process (defined as an AC1 of less than 0.9), it indicates the need for a larger proportion of records to be dual-screened.

@@

Data extraction was performed using a piloted data extraction form. Extracted items included: article metadata (year of publication, author, journal), study characteristics (study location, data source, exposure, outcomes, diagnostic criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value). I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.

@@

This was particularly relevant to preprints and published papers reporting the same study, which were not considered to be duplicate records but instead different reports of the same study. This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.

@@

\begin{equation}
SD = \sqrt{\frac{(N_1-1)SD_1^2 + (N_2-1)SD_2^2 + \frac{N_1N_2}{N_1 + N_2}(M_1^2 + M_2^2 - 2M_1M_2)}{N1 + N2 -1}}
  (\#eq:combiningGroups3)
\end{equation}

This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script employed to combine the groups for analysis.

@@

where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.[@rugge2011] The choice of _mg/dL_ was influenced by the widely-used categorises of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).

@@

Where additional data not reported by an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted. This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]

@@

Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result. Acceptable judgements for each domain include: "low risk", "some concerns", "high risk". Each of the five domains contains a series of signaling questions or prompts which guide the user through the tool. Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: bias due to confounding, bias due to selection of participants, bias in classification of interventions, bias due to deviations from intended interventions, bias due to missing data, bias in measurement of outcomes, and bias in selection of the reported result. Similar to RoB 2, it has a number of signaling questions which inform the domain-level judgement, with acceptable judgements including “low”, “moderate”, “serious” and “critical”. In the context of the tool, observational studies are assessed in reference to an idealised randomised controlled trial. Under this approach, the (rare) overall judgement of "low" indicates that the results should be considered equivalent to that produced by a randomised controlled trial.

While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] it was insufficiently developed at the time the risk-of-bias assessments for this review were performed. Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of bias as ROBINS-I, were made at the domain level. The motivation for using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS. Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs as part of this review.

@@

At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors).[@spiga2021] A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification. Acceptable judgements for each of the five domains in the tool were "low", "moderate" and "high" risk of bias.

@@

In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level. This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned analyses - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.

This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence. This is largely because the tool did not exist when the protocol was registered.

@@

I used a random-effects model in all meta-analyses.[[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$. The weight ($w$) assigned to each result (denoted as $y_i$) is then given as the inverse of the variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$. Once the weights are calculated for each result, the overall estimate ($\hat{y}$) and variance ($Var(\hat{y})$) can be estimated:

@@

Results included in a meta-analysis were stratified into subgroups on the basis of the overall risk of bias judgement, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate. Finally, where at least 10 results are available, a test of subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).[@deeks2019] All models were implemented using the `metafor` R package.[@R-metafor]

@@

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups. In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels. This marks a departure from the published protocol, as I was unaware that such a large number of studies would report dementia risk across multiple lipid categories.

@@

Restricted cubic spline models use "knots" to separate the data into subsets or "windows", in which the trend is modelled. Further restrictions are then imposed, in that the curves in each window must join up "smoothly" at the knot location, and that the trend is assumed to be linear before the first knot and after the last knot.[@gauthier2020] The locations of the knots in the model were identified using fixed percentiles (5th, 50th, 95th) of the exposure data.[@durrleman1989] Once the within-study trends have been estimated, they are combined in a multivariate random-effects meta-analysis using the restricted maximum likelihood (REML) method.[@liu2009; @white2009;@gasparrini2012] All dose-response analyses were implemented using the `dosresmeta` R package.[@crippa2016]

@@

One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond. This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool. Unless otherwise stated in the figure caption, only a single effect measure (hazard ratio/odds ratio/etc) is represented in the forest plot.

@@

Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)). As an adjunct analysis to this review, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis. In addition, in meta-analysis including at least one preprinted result, I assessed the impact of including the preprinted results on the summary estimate using a leave-one-out approach.

@@

Additionally, I followed identified preprints up after a two-year lag to investigate whether they had been subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or not (in which case preprints provide a distinct evidence source to conventional bibliographic databases).

@@

* I have detailed how this review will find, extract, critically assess and synthesize the results of existing studies. Additionally, I have highlighted how this review will examine the impact the of including preprinted results, as enabled by the research tool presented in the previous chapter.

>>>>

This analysis sought to address two specific aims. Firstly, as discussed in the introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship between lipids and dementia exist. These include randomised controlled trials, observational studies of different design, and Mendelian randomisation studies. However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types. Collating these diverse evidence sources is important, as, if the observed association between lipids and dementia is constant across them, it increases our confidence in the association. As such, the primary aim of this analysis was to systematically review all available literature describing prospective analyses, regardless of study design.

Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but can report relevant unpublished analyses. As a sensitivity analysis to the review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).

@@

Eligible studies screened participants for dementia at baseline and excluded any prevalent cases. Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate. No limits were placed on the sample size of included studies. Eligible studies defined dementia outcomes according to recognised criteria. Examples of acceptable criteria included the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the sole exception to this, as it was assumed that health care professionals employed their own expertise when entering the outcome into the EHR.

Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain relevant additional information not available from the abstract. No limitations were imposed on publication status, date, venue or language.

@@

Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) and studies where there was no screening for dementia at baseline were excluded. An exception to the latter criteria was made if the sample was initially assessed in mid-life (i.e. below the age of 50) were excluded. Additionally, studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arm were excluded. For example, a study examining exercise + statins versus statins alone would be excluded, but a study examining exercise + statins vs exercise alone would be eligible as the effect of statins can be estimated. Finally, studies using a dietary intervention, for example an omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet. Note that this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.

@@

When searching the bibliographic databases, study design filters (Lines 9-11 in Table \@ref(tab:searchOverview-table)) were employed to try to reduce the screening load. To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.

@@

Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. In addition, the abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range --> Finally, the reference lists of included studies were searched by hand, while forward and reverse citation searching ("snowballing") was performed using Google Scholar.[@greenhalgh2005; @wohlin2014]

@@

Records were imported into Endnote and de-duplicated using the method outlined in Bramer et al. (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates. The initial step involves automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), and is followed by manual review of articles with less overlap (e.g. those identified as duplicates based on the "Title" field alone).

Following de-duplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote and Rayyan. Endnote is a citation management tool,[@hupe2019] and Rayyan is a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. Additionally, I re-screened the same ~10% sample with 3 month lag to assess intra-rater consistency.

Similarly, I completed all full-text screening, with a random ~20% being screened by a second reviewer. Additionally, any records I identified as being difficult to assess against the inclusion criteria were also screened by the second reviewer. Reasons for exclusion at this stage were recorded. Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague. A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]

@@

Interpretion of agreement coefficients is a widely debated topic, and while arbitrary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement. Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrates an issue with the screening process (defined as an AC1 of less than 0.9), it indicates the need for a larger proportion of records to be dual-screened.

@@

Data extraction was performed using a piloted data extraction form. I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team. Extracted items included:

* Article metadata: year of publication, author, journal)
* Study characteristics: study location, data source, exposure, outcomes, diagnostic criteria used)
* Patient characteristics: age, sex, baseline cognition scores, baseline education scores
* Results: exposure, outcome, effect measure, effect estimate, error estimate, p-value).

@@

This was particularly relevant to preprints and published papers reporting the same study, which were not considered to be duplicate records but instead different reports of the same study. This decision was taken due to the potential for the published version to offer some information that the preprint did not, and vice versa.

@@

\begin{equation}
SD = \sqrt{\frac{(N_1-1)SD_1^2 + (N_2-1)SD_2^2 + \frac{N_1N_2}{N_1 + N_2}(M_1^2 + M_2^2 - 2M_1M_2)}{N1 + N2 -1}}
  (\#eq:combiningGroups3)
\end{equation}
&nbsp;

where $N_i$, $M_i$ and $SD_i$ denote the number of participants, mean and standard deviation in the $i$th subgroup. This approach was implemented in a systematic manner, with the raw group data being extracted and a cleaning script employed to combine the groups for analysis.

@@

where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.[@rugge2011] The choice of _mg/dL_ was influenced by the widely-used categories of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).

@@

Where additional data, not included in the report of an analysis, were required either for data extraction or risk-of-bias assessment, the corresponding author of the study was contacted. This approach was taken due to the potentially large impact of additional information obtained through contact with study authors on the results of the review.[@reynders2019]

@@

Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains:

* bias arising from the randomization process, 
* bias due to deviations from intended intervention, 
* bias due to missing outcome data, 
* bias in measurement of the outcome, 
* bias in selection of the reported result.

Acceptable judgements for each domain include: "low risk", "some concerns", "high risk". Each of the five domains contains a series of signaling questions or prompts which guide the user through the tool. Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains:

* bias due to confounding, 
* bias due to selection of participants, 
* bias in classification of interventions, 
* bias due to deviations from intended interventions, 
* bias due to missing data, 
* bias in measurement of outcomes, and 
* bias in selection of the reported result.

Similar to RoB 2, it has a number of signaling questions which inform the domain-level judgement, with acceptable judgements including “low”, “moderate”, “serious” and “critical”. In the context of the tool, observational studies are assessed in reference to an idealised randomised controlled trial. Under this approach, the (rare) overall judgement of "low" indicates that the results should be considered equivalent to that produced by a randomised controlled trial.

While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] it was insufficiently developed at the time the risk-of-bias assessments for this review were performed. Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of risk of bias as ROBINS-I, were made at the domain level. The motivation for using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS. Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs as part of this review.

@@

At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomization studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies.[@spiga2021] Advanced results from this review were obtained from contact with the review authors. A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification. Acceptable judgements for each of the five domains in the tool were "low", "moderate" and "high" risk of bias.

@@

In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level. This assessment examines evidence missing due to selective non-reporting as distinct from the selective reporting of a single result from multiple planned analyses. The assessment was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.

This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try to examine the risk of bias due to missing evidence. This is largely because the tool did not exist when the protocol was registered.

@@

I used a random-effects model in all meta-analyses.[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$. The result in the $i$th study is denoted as $y_i$. The weight assigned to this result is then given as the inverse of the variance of that result ($v_i$) plus the estimate of between-result variance ($\tau^2$):

\begin{equation}
w_i = \frac{1}{v_i+\tau^2}
  (\#eq:ivweighting)
\end{equation}

Once the weights are calculated for each result, the overall estimate ($\hat{y}$) and variance ($Var(\hat{y})$) can be estimated:

@@

Results included in each meta-analysis were stratified into subgroups on the basis of the overall risk of bias judgement, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate. Finally, where at least 10 results are available, a test of subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).[@deeks2019] All models were implemented using the `metafor` R package.[@R-metafor]

@@

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups. In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels. This marks a departure from the published protocol, as I had not expected the number of studies reporting dementia risk across lipid sub-categories to be sufficient for a dose response analysis.

<!-- TODO Maybe rephrase last sentence -->

@@

Restricted cubic spline models use "knots" to separate the data into subsets or "windows", in which the trend is modelled. Further restrictions are then imposed, in that the curves in each window must join up "smoothly" at the knot location, and that the trend is assumed to be linear before the first knot and after the last knot.[@gauthier2020] The locations of the knots in the model were identified using fixed percentiles (5th, 50th, 95th) of the exposure data.[@durrleman1989] Once the within-study trends had been estimated, they were combined in a multivariate random-effects meta-analysis using the restricted maximum likelihood (REML) method.[@liu2009; @white2009;@gasparrini2012] All dose-response analyses were implemented using the `dosresmeta` R package.[@crippa2016]

@@

One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond. This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool. Unless otherwise stated in the figure caption, only a single effect measure (hazard ratio/odds ratio/etc) is represented in the forest plot.

@@

Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)). As an adjunct analysis to this review, meta-analyses including a preprint result were re-analysed using a fixed effect model. The weight assigned to the preprinted result was extracted and used to assess the additional evidential value provided by the preprint. In addition, in meta-analysis including at least one preprinted result, I assessed the impact of including the preprinted results on the summary estimate using a leave-one-out approach.

@@

Additionally, I performed a follow-up analysis, allowing for a a two-year lag, to investigate whether identified preprints had been subsequently published (in which case preprints provided a snapshot into the future, and a systematic review update would capture the published version of the preprint) or not (in which case preprints provide a distinct evidence source to conventional bibliographic databases).

@@

* I have detailed how this review will find, extract, critically assess and synthesize the results of existing studies. Additionally, I have highlighted how this review will examine the impact of including preprinted results, as enabled by the research tool presented in the previous chapter.
